VariantSpark: Population Scale Clustering of Genotype Information

### 2015-09-15 doc/publications/journal2014/paper.tex

%% TODO - NEIL - (and better heading) %%
\subsection*{Personal Genome Project VCF making}
The PGP data.....

>>>>

%% TODO - NEIL - (and better heading) %%
\subsection*{Personal Genome Project Data}
%% The PGP data..... 
PGP genome data was downloaded from the PGP website (\url{https://my.pgp-hms.org/public_genetic_data}). Genotype data from 23andMe microarray platforms was sorted by genome 
build. Those files corresponding to NCBI build 36 were converted to BED format, updated to build 37 using UCSC liftOver and then converted back to 23andMe format. The 
23andMe files were then converted to VCF format using code obtained from the Broad Institute (\url{http://apol1.blogspot.com.au/2013/08/impute-apoe-and-apol1-with-23andme.html}). 
Where individuals had genotype data for both genome builds 36 and 37, only the latter was used. Finally, individual VCF files were combined for clustering into one 
file using VCFtools \cite{Danecek2011Variant}.

[if code to be made available, say so here and where it will be]
